### 2020-11-28 paper/sections/design.tex
update introduction and using a new figure2
minor figure 2

\begin{figure*}[!t]
	\centerline{\includegraphics[width=0.9\linewidth]{figures/DQN.jpg}}
	%	\vspace{0.2cm}
	\caption{Applying reinforcement learning to automatic configuration.\textcolor{note}{redo}}
	\label{fig: DQN}
\end{figure*}

Figure~\ref{fig: DQN} summarizes how RL can be applied to automatic configuration. Briefly, it is a reinforcement learning-based system to train an agent to choose a proper configuration $ c $ for one video chunk to be inferenced. We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback in the following subsections. We provide experimental details of all the hyperparameters in Section~\ref{Section: experiment}. %% \\

@@

For the cost of the object detection service, we use average GPU processing time per frame as the metric of resource consumption, because GPU is the dominant resource for the majority of video processing workloads. We also denote the metric of resource consumption as $ \hat{s}_{ic} $ that for an input video chunk $ x_i $ and a given configuration $ c $. For a reference configuration $ c_{\rm ref} $, the reference resource consumption is $ \hat{s}_{\rm ref} $.

@@

The RL agent is expected to give a proper configuration $ c $ for minimizing the resource consumption $ \hat{s}_c $ while keeping the accuracy $ \mathcal{A} $. For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $. Therefore we can use the Deep Q-learning Network \cite{DQN} as the RL agent. But the naive Deep Q-learning Network can not work well in this task, because the state space of reinforcement learning is too large if we directly treat video chunk as the input. To preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge.  
%because of the following challenges: %% \\
%
%\begin{itemize}
%	\item The state space of reinforcement learning is too large. To preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge. 
%	\item It takes a long time to train one step in a large inference neural network, making the training process too time-consuming.
%	\item The RL agent starts training from random trials and learns afterward from the reward feedback. When training from a randomly initialized neural network, the reward feedback is very sparse, making it difficult for the agent to learn.
%\end{itemize}

>>>>

\begin{figure*}[!t]
	\centerline{\includegraphics[width=0.9\linewidth]{figures/framework2.pdf}}
	%	\vspace{0.2cm}
	\caption{Applying reinforcement learning to automatic configuration}
	\label{fig: DQN}
\end{figure*}

Figure~\ref{fig: DQN} summarizes how RL can be applied to the automatic configuration. Briefly, it is a reinforcement learning-based system to train an agent to choose a proper configuration $ c $ for one video chunk to inference. We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback in the following subsections. We provide experimental details of all the hyperparameters in Section~\ref{Section: experiment}. %% \\

@@

For the cost of the object detection service, we use average GPU processing time per frame as the metric of resource consumption because GPU is the dominant resource for the majority of video processing workloads. We also denote the metric of resource consumption as $ \hat{s}_{ic} $ that for an input video chunk $ x_i $ and a given configuration $ c $. For a reference configuration $ c_{\rm ref} $, the reference resource consumption is $ \hat{s}_{\rm ref} $.

@@

The RL agent is expected to give a proper configuration $ c $ for minimizing the resource consumption $ \hat{s}_c $ while keeping the accuracy $ \mathcal{A} $. For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $. Therefore we can use the Deep Q-learning Network \cite{DQN} as the RL agent. But the naive Deep Q-learning Network can not work well in this task because the state space of reinforcement learning is too large if we directly treat video chunk as the input. To preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge.  
%because of the following challenges: %% \\
%
%\begin{itemize}
%	\item The state space of reinforcement learning is too large. To preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge. 
%	\item It takes a long time to train one step in a large inference neural network, making the training process too time-consuming.
%	\item The RL agent starts training from random trials and learns afterward from the reward feedback. When training from a randomly initialized neural network, the reward feedback is very sparse, making it difficult for the agent to learn.
%\end{itemize}
